### 2024-06-17 basic-statistics.qmd
20240616 - consistency
20240616 - clarification

Indices to describe the *variability* of a variable's data include:

@@

where $T$ is the test statistic of interest (e.g., $t$-, $r-$, $F$-, or $B$-coefficient, depending on the test) and $t$ is the observed test statistic.

>>>>

Indices to describe the *spread* (variability) of a variable's data include:

@@

where $T$ is the test statistic of interest (e.g., the distribution of $t$-, $r-$, or $F$ values, depending on the test) and $t$ is the observed test statistic (e.g., $t$-, $r-$, or $F$-coefficient, depending on the test).
